---
title: "Alcohol vs Seat choice"
author: "Kathleen Giba"
date: "September 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data
$H_O$: There is no difference among the mean amount of alcohol consumed per week by row.  
$H_A$ There is a difference in alcohol amount consumed per week per row.  
```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata )
```
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```
  
## Conclusions    

It appears from the TukeyHSD that there there is a difference in the amount of alcohol consumed. when sitting in the Middle-Front you consumed.  Where sitting in the front-back or Middle back there is no really big difference.   

The P value is less than 0.05, therefore the null hypothesis is extremely unlikely; we reject the null hypothesis.  

We conclude that there is a difference, that if you sit in the Middle-Front instead of the Front-Back or Middle-Back you tend to drink more.